Safe Memory Regions for Big Data Processing

### 2016-10-10 paper/type-inference.tex
type inference proof

\begin{lemma}
Let $C = \consOf{q}$.
Suppose a region variable $\rho$ is bound to two different region constants $\pi_1$
and $\pi_2$ in $\satC$.
Let $\soln$ satisfy $\satC$.
For any context $\varphi \conj \phi$ that contains $\rho$, we must have
$\{ \pi_1, \pi_2 \} \subseteq \predDeltaMap(\varphi)$ and
$\isvalid{\predSubstFn(\varphi)}{\pi_1 = \pi_2}$.
\end{lemma}

@@

\begin{proof}
If $\satC$ is satisfiable, then $\groundC$ is trivially satisfiable.
We just need to show that the definition $\regionSubstFn(\rho)$ for any
region variable $\rho$ will succeed.
\end{proof}

>>>>

\begin{lemma}
Let $C = \consOf{q}$.
Suppose a region variable $\rho$ is bound to two different region constants $\pi_1$
and $\pi_2$ in a context $\varphi \conj \phi$. % in $\satC$.
Let $\soln$ satisfy $\satC$.
For any context $\varphi \conj \phi$ that contains $\rho$, we must have
$\{ \pi_1, \pi_2 \} \subseteq \predDeltaMap(\varphi)$ and
$\isvalid{\predSubstFn(\varphi)}{\pi_1 = \pi_2}$.
\end{lemma}

@@

\begin{proof}
If $\satC$ is satisfiable, then $\groundC$ is trivially satisfiable.
If $\groundC$ is satisfiable, the solver will fail to return an assignment only if the set $S_\rho$ = 
$\{ \pi \in \regionDeltaMap(\rho) \; | \; \isvalid{\ell}{\rho = \pi} \in \satC \}$ is empty for some region variable $\rho$.
Consider any such $\rho$.
Let $\soln$ be a satisfying assignment for $\satC$.
Let $\pi' = \predSubstFn(\rho)$. Then, we must have $\pi' in \regionDeltaMap(\rho)$.
From Lemma~\ref{lemma:completely-bound}, $\rho$ must be bound to some $\pi$ in some context $\ell$.
Thus, $\isvalid{\ell}{\rho = \pi} \in \satC$.
Since $\soln$ satisfies this constraint, we have $\isvalid{\ell[\soln]}{\pi' = \pi}$.
If $\pi$ and $\pi'$ are the same region identifier, we have a contradiction, since
$\pi \in S_\rho$ and $S_\rho$ cannot be empty.
If $\pi$ and $\pi'$ are distinct region identifiers, then it follows that the precondition of case (a) must hold
in Lemma~\ref{lemma:decomposition}, and we must have $\{ \pi, \pi' \} \subseteq \predDeltaMap(\varphi)$.
We can show, by induction over the constraint-generation rules, that if $\regionDeltaMap(\rho)$ includes
some element of $\predDeltaMap(\varphi)$, then it includes all elements of $\predDeltaMap(\varphi)$.
It follows that $\pi \in \regionDeltaMap(\rho)$. Hence, the set $S_\rho$ is non-empty (as it contains $\pi$.
The result follows.
\end{proof}
